---
title: "Assessment 1"
author: "Fahmida Islam s4669637"
date: "16/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



#RMarkdown editing
**Easier for human to understand** - *The report generated by RMarkdown makes it easier for human to understand the content of a webpage or big report as it explains and displays the report with the help of the data visualisation.RMarkdown offer an environment where one can easily write the complete code as chunks of code, analysis and presents. *

##Please refer below for the dataset that I will be using here for the assessment.

Click [Here](https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv)

##Completed all parts of question 1

##Created the section called RMarkdown editing as above for question 2

##Have written few sentences about RMarkdown for question 3

##Utilized **bold** and *Italic* form for editing for question 4

##Revied the recommended documentatuion for for inserting link within the .rmd file for question 5

Loading the packages

```{r}
library(tidyverse)
library(knitr)
library(skimr)
```



---------------------------------------------------------------------------
**Q-6 Insert an R chunk and create a variable with this dataset
https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv **

```{r}
#Inserting R chunk and creating variable with Dataset

fastfood <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
glimpse("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```

**Q-7 Display the first 10 rows of the dataset using head() and kable(). 

Display the first 10 rows of the dataset and the first 5 variables

Use Help and the link below to read more about those functions  https://bookdown.org/yihui/rmarkdown-cookbook/kable.html** 

```{r}
#Presenting the 1st ten rows of the dataset utilizing kable and head function

fastfood %>% head(10)

knitr::kable(head(fastfood[1:10,1:5]), "pipe")
 
kable(fastfood[1:10, 1:5]) 
```

**Q-8 Display the observations that has more than 1000 calories**

```{r}
#Presenting the obesrvations which is having above 1000 calories

fastfood %>%
  filter(calories>1000)
```

**Q-9  Arrange observations with more than 40 in total_fat and more than 80 in total_carb in the descending order and save them to a new variable (dataset) called `dont_eat_this`**

```{r}
#Providing the solution below for the above question. However,logically it is not possible to arrange both total_fat and total_carb in descending order at the same time. Only one can be done at a given point of time

dont_eat_this<-fastfood
dont_eat_this %>%
  filter(total_fat>40,total_carb>80)%>%
  arrange(desc(total_fat))
```

**Q-10  Using the initial dataset variable, use `case_when()` to create a new variable `heavy_food` which is equal to "heavy" when total calories are greater than 500, "low" when total calories are less than 250 and "average" for all other cases. Count the number of observations in each created category.**

```{r}
#Providing the solution below for the above question

heavy_food <- fastfood
heavy_food %>%
mutate(heavy_food = case_when(calories > 500 ~ "heavy",
                              calories < 250 ~ "low",
                              T ~ "average"))
```

**Q-11 Display the types of variables in the dataset using `skimr` package**

```{r}
#Providing the solution below for the above question

skim(heavy_food)
```

**Q-12 Present the count observations from each restaurant in a descending order

Show the number of distnct items on a menu in the dataset**

```{r}
#Providing the solution below for the above question

fastfood%>%
  count(restaurant)%>%
  arrange(desc(n))

fastfood %>%
  n_distinct(fastfood $ item)
```

**Q-13 Using groupings (group_by()), summarise and display the average number of calories for each restaurant.**

```{r}
#Providing the solution below for the above question

fastfood %>%
  group_by(calories) %>%
  summarise(average_number_calories = mean(calories)) %>%
  ungroup ()

```

**Q-14 Add variables to the dataset, which:

-  calculates the average calories per type of restaurant and call it `average_calories` 
-  calculates the maximum total_fat per type of restaurant and call it `max_fat` 
-  calculates the minimum cholesterol per type of restaurant and call it `min_cholesterol` **

```{r}
#Providing the solution below for the above question

fastfood %>%
  group_by(restaurant)%>%
  summarise(average_calories = mean(calories)) %>%
  ungroup()

fastfood %>%
  group_by(restaurant)%>%
  summarise(max_fat = max(total_fat)) %>%
  ungroup()

fastfood %>%
  group_by(restaurant)%>%
  summarise(min_cholesterol = min(cholesterol)) %>%
  ungroup()
```

**Q-15 Display the data vis of total fat per each type of restaurant. Write a narration (2-3 sentences) why you believe this type of data viz presents such information best.**

```{r}
#Providing the solution below for the above question.Initially I did it on Point graph as showed below.However, I have found that the information gets hard to read on. Therefore, I have ended up with the bar chart to visualize the given data as it gets easier to read through bar chart.Therefore the 
ggplot(fastfood, aes(restaurant, total_fat)) +
  geom_point() +
  coord_flip()

#The appropriate one is given below. The one above is for example only to demonstrate how it shows in Bar chart.

ggplot(fastfood, aes(restaurant, total_fat)) + 
  geom_bar(stat = 'identity')

```

**Q-16 Add a variable to the dataset, which calculates the sum of cholesterol and sodium and call it `cholesterol_sodium`.

Remove the variable `salad`**

```{r}
#Providing the solution below for the above question

cholesterol_sodium <- fastfood
cholesterol_sodium %>%
  mutate(cholesterol_sodium = sum(cholesterol,sodium)) %>%
  select(-salad)
```

**Q-17 Use observations for Mcdonalds to plot sugar variable against protein with `geom_point()` **

```{r}
#Providing the solution below for the above question

fastfood %>%
  filter(restaurant == "Mcdonalds") %>% 
  ggplot(aes(sugar, protein)) + 
  geom_point()

```

**Q-18 Identify variable(s) which should be factors and transform their type into a factor variable.**

```{r}
#Providing the solution below for the above question

str(fastfood)
fastfood $ restaurant <- as.factor(fastfood $ restaurant)
skim(fastfood)
  

```


**Q-19 Create two new variables:

Read about `cut_number()` function using Help and add a new variable to the dataset `calories_type`. Use `calories` variable for `cut_number()` function to split it into 3 categories `n=3`, add labels `labels=c("low", "med", "high")` and make the dataset ordered by arranging it according to calories. 

Do not forget to save the updated dataset.** 

```{r}
#Providing the solution below for the above question

calories_type <- fastfood
calories_type %>%
  mutate(calories_type = cut_number(calories,n=3,labels = c("low","med","high"))) %>%
  arrange(calories)
```

**Q-20 Create a dataviz that shows the distribution of `calories_type` in food items for each type of restaurant. Think carefully about the choice of data viz. Use facets, coordinates and theme layers to make your data viz visually appealing and meaningful. Use factors related data viz functions.**

```{r}
#Providing the solution below for the above question

calories_type %>%
  count(calories, restaurant) %>%
  ggplot(aes(restaurant,calories)) +
  geom_point(colour = "blue") +
  coord_flip()

```


**Q-21 The second variable should show the percentage of `trans_fat` in `total_fat`. Add the variable to the dataset and call it `trans_fat_percent`. Do not forget to save the updated dataset.** 

```{r}

#Providing the solution below for the above question

trans_fat_percent <- fastfood
trans_fat_percent %>%
  mutate(trans_fat_percent = trans_fat/total_fat * 100)
```

**Q-22 Create a dataviz that shows the distribution of `trans_fat` in food items for each type of restaurant. Think carefully about the choice of data viz. Use facets, coordinates and theme layers to make your data viz visually appealing and meaningful.**

```{r}
#Providing the solution below for the above question

ggplot(fastfood, aes(restaurant, trans_fat, fill = restaurant)) + 
  geom_col() +
  theme_linedraw()
```


**Q-23 Calculate and show the average (mean)  `total_fat` for each type of restaurant. No need to save it as a variable.**

```{r}
#Providing the solution below for the above question

fastfood %>%
  group_by(restaurant)%>%
  summarise(average_total_fat = mean(total_fat)) %>%
  ungroup()
```


**Q-24 And create a dataviz that allow to compare different restaurants on this variable (`total_fat`). You can present it on one dataviz (= no facets). 

Think carefully about the choice of data viz. Use coordinates and theme layers to make your data viz visually appealing and meaningful. **

```{r}

#Providing the solution below for the above question

ggplot(fastfood, aes(restaurant, total_fat, fill = restaurant)) +
  geom_col() +
  theme_linedraw()
```

